### 2018-01-25 pubs/itp-2018/sections/abstract.tex
ITP 2018: Initial commit.
[ itp-2018 ] Abstract and title submitted.

\begin{abstract}

We describe a syntactical proof-reconstruction approach to verify
derivations generated by \Metis prover to theorems in classical
propositional logic. To verify such derivations, we formalise in type
theory each inference rule of the \Metis reasoning. We developed a
tool jointly with two \Agda libraries to translate \Metis derivations
to \Agda proof-terms. These developments allowed us to type-check
with \Agda, \Metis derivations step-by-step.

\keywords{proof-reconstruction, type theory, automatic theorem prover,
proof-assistant}
\end{abstract}

>>>>

\begin{abstract}
  We describe a syntactical proof-reconstruction approach to verify
  derivations generated by the automatic theorem prover \Metis for
  classical propositional logic theorems. To verify these derivations,
  we use \Agda, a proof assistant for dependent type theory. We
  formalise in \Agda each inference rule of \Metis reasoning, that is,
  we transform \Metis derivations into \Agda proof-terms. In a future
  full-fledged integration of \Agda with off-the-shelf automatic
  theorem provers, proof-reconstruction shall be a necessary
  component.

  \keywords{proof-reconstruction, automatic theorem provers,
    proof-assistants, Agda, Metis}
\end{abstract}
